### 2012-02-15 paper.tex
Initial corrections after Ibs comments

\noindent\large{\textbf{Robert Jensen\textit{$^{b}$}, Thomas Andersen\textit{$^{b}$}, Anders Nierhoff\textit{$^{b}$}, Søren Dahl\textit{$^{b}$}, Ole Hansen\textit{$^{b}$} and Ib Chorkendorff\textit{$^{a}$}}}\vspace{0.5cm}
%Please note that \ast indicates the corresponding author(s) but no footnote text is required.

@@

\begin{figure}[h]
\centering
  \includegraphics[width=9cm]{temperature_dependence.png}
  \caption{After about 10 hours of oscillations at 205$^\circ$C the temperature is first lowered by 5$^\circ$C and soon after increased by 2$^\circ$C. Before the temperature step the oscillation period was approximately 500\,s and after the step the period is approximately 5000\,s.}
  \label{fgr:temperature_dependence}
\end{figure}
A very strong temperature dependence on the oscillation frequency was also found as shown in Figure~\ref{fgr:temperature_dependence}. By changing the temperature 5$^\circ$C the oscillation period is changed by more than a factor of 10. The magnitude of the change is not completely consistent across all measured samples but all samples do show a very large temperature dependency where in some cases a provoked small change in temperature will consistently turn on and off the oscillations.

@@

Although a range of different CO/O$_2$ ratios were tried no oscillations could be provoked on thin films of comparable geometrical coverage to the nanoparticles in our system. This is not, however, believed to be a property of the platinum thin film but a property of the small reactor used in this study. This is supported by literature where oscillations have been observed on both extended thin-films \cite{Singh2010} as well as on single crystals \cite{Hendriksen2005} at atmospheric pressure.

@@

According to the proposed model the bare metal surface is less active than the oxidized surface. It is further suggested that a high concentration of steps will thermodynamically favor the reduced surface and a low concentration of steps will favor the oxidized surface. The oscillating behavior is hence attributed to the shift between an oxidized surface which will increase surface roughness and a reduced surface which will decrease surface roughness. Thus, the reaction will only run a given time in the high-rate state before the catalyst will expose the reduced surface and lower the rate. After some time, the roughness will again be sufficiently low that the catalyst will again oxidize and increase the rate.

In this study Pt nanoparticles were investigated which, compared to a single crystal or a thin film, is a very rough surface. It is to be expected that the particles will initially favor the reduced state. As the reaction runs, the conditions toward the outlet of the reactor will become more reducing and at the same time the reaction itself will smoothen the particles further pushing towards an oxidation of the particles. Gradually as the particles toward the outlet oxidizes the turn-over will increase and the general CO concentration will decrease promoting more and more particles to oxidize which will gradually be seen in the mass-spectrometry as an increase in CO$_2$ and a decrease in CO.

Even though the temperature is kept constant the light-off temperature will decrease as the CO-concentration increases. At a given point the CO concentration will become low enough that the light-off temperature drops below the sample temperature and the sample will show full conversion. If not all particles are oxidized at this point they will oxidize much faster after light-off due to the low CO-concentration. The further increased rate will not be visible in the mass-spectrometer since the reactor is already in full conversion. As most of the particles are now oxidized they will become more and more roughened and gradually return to the reduced state. Fewer and fewer oxidized particles will be responsible for the activity increasing the roughness rate of the remaining active particles. Just before the overall activity drops only a very small fraction of the particles actually participates in the reaction and the deactivation will happen very suddenly once these few particles eventually becomes sufficiently rough that they will reduce and lose activity.

@@

>>>>

\noindent\large{\textbf{Robert Jensen\textit{$^{a}$}, Thomas Andersen\textit{$^{a}$}, Anders Nierhoff\textit{$^{a}$}, Thomas Pedersen\textit{$^{b}$}, Ole Hansen\textit{$^{b}$}, Søren Dahl\textit{$^{a}$} and Ib Chorkendorff\textit{$^{a}$}}}\vspace{0.5cm}
%Please note that \ast indicates the corresponding author(s) but no footnote text is required.

@@

\begin{figure}[h]
\centering
  \includegraphics[width=9cm]{temperature_dependence.png}
  \caption{After about 10 hours of oscillations at 205$^\circ$C the temperature is first lowered by 5$^\circ$C and soon after increased by 2$^\circ$C. Before the temperature step the oscillation period was approximately 500\,s and after the step the period is approximately 5000\,s.}
  \label{fgr:temperature_dependence}
\end{figure}
A very strong temperature dependence on the oscillation frequency was also found as shown in Figure~\ref{fgr:temperature_dependence}. By changing the temperature 5$^\circ$C the oscillation period was changed by more than a factor of 10. The magnitude of the change is not completely consistent across all measured samples but all samples do show a very large temperature dependency where in some cases a provoked small change in temperature will consistently turn on and off the oscillations.

@@

Although oscillations have been observed on extended platinum thin films \cite{Singh2010} as well as single crystals\cite{Hendriksen2005} at atmospheric pressure no oscillations could be provoked on thin films of comparable geometrical coverage to the nanoparticles in our system at any CO/O$_2$ ratio.

@@

According to the proposed model the bare metal surface is less active than the oxidized surface. It is further suggested due to the general high adsorption energy of CO on metal surfaces that CO stabilizes a metal surface stable at low CO concentrations on high-density stepped surfaces. Contrary, a low concentration of steps will favour an oxidized surface. The oscillating behavior is hence attributed to the shift between an oxidized surface which will increase surface roughness and a reduced surface which will decrease surface roughness. Thus, the reaction will only run a given time in the high-rate state before the catalyst will expose the reduced surface and lower the rate. After some time, the roughness will again be sufficiently low that the catalyst will again oxidize and increase the rate.

In this study Pt nanoparticles were investigated which, compared to a single crystal or a thin film, is a very rough surface. It is to be expected that the particles will initially favor the reduced state. As the reaction runs, the conditions toward the outlet of the reactor will become more oxidizing and at the same time the reaction itself will smoothen the particles further pushing towards an oxidation of the particles. Gradually as the particles toward the outlet oxidizes the turn-over will increase and the general CO concentration will decrease promoting more and more particles to oxidize which will gradually be seen in the mass-spectrometry as an increase in CO$_2$ and a decrease in CO.

Even though the temperature is kept constant the light-off temperature will decrease as the CO-concentration decreases. At a given point the CO concentration will become low enough that the light-off temperature drops below the sample temperature and the sample will show full conversion. If not all particles are oxidized at this point they will oxidize much faster after light-off due to the low CO-concentration. The further increased rate will not be visible in the mass-spectrometer since the reactor is already in full conversion. As most of the particles are now oxidized they will become more and more roughened and gradually return to the reduced state. Fewer and fewer oxidized particles will be responsible for the activity increasing the roughness rate of the remaining active particles. Just before the overall activity drops only a very small fraction of the particles actually participates in the reaction and the deactivation will happen very suddenly once these few particles eventually becomes sufficiently rough that they will reduce and lose activity.

@@

Noget om turnover frequency??
